---
title: "data cleaning 2"
output: html_document
date: "2023-01-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#read in data
data <- read.csv("data.csv", na.strings=c("","NA"))

library(dplyr)
library(tidyr)
library(tidyverse)
library(ggplot2)
library(broom)
library(lsr)
library(effsize)
library('cowplot')

#mediation package
library(bmlm)
```




















////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
CLEANING DATA & DEMOGRAPHICS
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////


```{r}
#### Remove rows #### 


  #e.g. no survey previous, no Finished = FALSE, feedback, progress = less than 100

#delete irrelevant columns
CHECKdata = data %>% select(-matches("First.Click|Last.Click|Page.Submit|Click.Count"))
  
#delete attention questions
CHECKdata = CHECKdata %>% select(-matches("Prolific_ID|Attention"))

#delete unfinished response ROWS
CHECKdata <- filter(CHECKdata,Status!="Survey Preview",Finished!="FALSE",Status!="Spam",DistributionChannel!="preview",data$Q89!="I do not agree to complete this survey",Status!="Response Type")
  	
#check new number
nrow(CHECKdata)
```

```{r}
#### Remove columns #### 


#delete above columns
dat <- subset(CHECKdata, select = -c(Status,Progress,Duration..in.seconds.,Finished,DistributionChannel,Q89))

#delete feedback columns
dat = subset(dat, select = -c(Problems.,problems.p2,Seen.Before.,Study.about.,Other.Feedback.))

#delete columns with identifying information
dat = subset(dat, select = -c(StartDate,EndDate,RecordedDate,RecipientLastName,RecipientFirstName,RecipientEmail,ExternalReference,LocationLatitude,LocationLongitude,UserLanguage) )



#rename FL_5_DO to "group" to indicate DFFD or FDDF group

dat <- dat %>% mutate(FL_5_DO=recode(FL_5_DO,'FL_20'='A','FL_21'='B'))

dat <- dat %>% dplyr::rename(group=FL_5_DO) 
```

```{r}
##### DEMOGRAPHICS #### 

#data frome for response id + demographics
demo <- dat %>% select(ResponseId,D1...gender,D2...age,D3...education,D4...fluent.,D5...ethnicity)

#delete demographics from dat
dat = subset(dat, select = -c(D1...gender,D2...age,D3...education,D4...fluent.,D5...ethnicity))
```


```{r}
#merge columns from group A and group B
datA <- dat %>% filter(group == 'A') %>% select(ResponseId:Q131_1, group) 
datB <- dat %>% filter(group == 'B') %>% select(ResponseId, Q99:group)
names(datB) <- names(datA)
datCombined <- rbind(datA,datB)

```

```{r}
#remove NA screenouts
df <- na.omit(datCombined)

#remove screenout Qs and put in new df
Sceenout <- select(df,Q63,Q64,Q65,Q66,Q67,Q68,Q69,Q70,Q71,Q72,Q73,Q74)
datNum <- select(df, -c(Q63,Q64,Q65,Q66,Q67,Q68,Q69,Q70,Q71,Q72,Q73,Q74))

nrow(datNum)
```

```{r}

#rename columns
datNum <- datNum %>% rename("H1"="Q1001_1",
                            "L1"="Q10002_1",
                            "O1"="Q1003_1",
                            "H2"="Q1005_1",
                            "L2"="Q1006_1",
                            "O2"="Q1007_1",
                            "H3"="Q125_1",
                            "L3"="Q126_1",
                            "O3"="Q127_1",
                            "H4"="Q129_1",
                            "L4"="Q130_1",
                            "O4"="Q131_1")
                          
```
renames for ratings:
  H - hireability 
  L - likeability
  E - ease of opinion



```{r}
#only retain demographic data from ppts in datNum dataframe

demo <- merge(datNum, demo, by.x = "ResponseId")
demo <- demo %>% select(ResponseId,D1...gender,D2...age,D3...education,D5...ethnicity)
```

```{r}
#check for any duplicate response IDs
datNum %>% count(ResponseId)
```


D1...gender

1 = male
2 = female
3 = nonbinary/third_gender
4 = prefer not to say

D3...education

1 = No formal education
2 = Secondary school (GCSEs/O levels or equivalent)
3 = Sixth form (A levels or equivalent)
4 = Undergraduate degree (BSc/BA or equivalent)
5 = Postgraduate degree (MSc/MA/MRES/PhD or equivalent)
6 = Prefer not to say

D5...ethnicity

1=White
2=Asian / Asian British
3=Black / African / Caribbean / Black British
4=Mixed / Multiple ethnic groups
5=Other
6=Prefer not to say

```{r}
##### summarise demographic information #####

#age
demo %>% summarise(meanAge=mean(D2...age), maxAge=max(D2...age), minAge=min(D2...age), sdAge=sd(D2...age))

#gender
  #recode and count
  demo <- demo %>% mutate(D1...gender=recode(D1...gender,'1'='male','2'='female','3'='nonbinary/third_gender','4'='prefer_not_to_say'))
demo %>% count(D1...gender)
  
#education
  #recode and count
  demo <- demo %>% mutate(D3...education=recode(D3...education,'1'='No_formalEdu','2'='Secondary','3'='Sixthform','4'='Undergraduate','5'='Postgraduate degree','6'='prefer_not_to_say'))
demo %>% count(D3...education)
  
#ethnicity 
  #recode and count
  demo <- demo %>% mutate(D5...ethnicity=recode(D5...ethnicity,'1'='White','2'='Asian','3'='Black','4'='Mixed','5'='Other','6'='prefer_not_to_say'))
demo %>% count(D5...ethnicity)


#total ppts
nrow(demo)


#count number of A and B responses 
table(datNum['group'])

```



```{r}
#make data type correct

#check what data looks like
print(typeof(datNum$H1))
str(datNum)

#convert chr to numeric

i <- c(2,3,4,5,6,7,8,9,10,11,12,13)  

datNum[ , i] <- apply(datNum[ , i], 2,  
                    function(x) as.numeric(as.character(x)))


```
#check change worked
str(datNum)


```{r}
#make dataset with sums accross scores

datCompNum <- datNum %>% mutate(H_Comp = H1+H2+H3+H4) %>% mutate(L_Comp = L1+L2+L3+L4) %>% mutate(O_Comp = O1+O2+O3+O4)
```

////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
END OF DATA CLEANING + demographics


































////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
DATA ANALYSIS
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////


Do a within groups t test

For each ppt average:
	average fluent ratings 
	average disfluent ratings 

So:
    group A (FDDF)
    Fluent = end videos = avarage H1 + H4
    Disfluent = middle videos = avarage H2 + H3
  
    group B (DFFD)
    Fluent = middle videos = avarage H2 + H3
    Disfluent = end videos = avarage H1 + H4
  

```{r}
#### setting up for within groups T test

#split df into A and B
datWithin_A <- datNum %>% filter(group == 'A') %>% select(ResponseId:group, group)
datWithin_B <- datNum %>% filter(group == 'B') %>% select(ResponseId:group, group)

#group A avarage scores

  # H fluent 
      datWithin_A <- datWithin_A %>% mutate(H_Fluent = (H1+H4)/2)
  # H disfluent
      datWithin_A <- datWithin_A %>% mutate(H_Disfluent = (H2+H3)/2)
      
  # L fluent 
      datWithin_A <- datWithin_A %>% mutate(L_Fluent = (H1+H4)/2)
  # L disfluent
      datWithin_A <- datWithin_A %>% mutate(L_Disfluent = (H2+H3)/2)
      
  # O fluent 
      datWithin_A <- datWithin_A %>% mutate(O_Fluent = (H1+H4)/2)
  # O disfluent
      datWithin_A <- datWithin_A %>% mutate(O_Disfluent = (H2+H3)/2)

#group B avarage scores

  # H fluent 
      datWithin_B <- datWithin_B %>% mutate(H_Fluent = (H2+H3)/2)
  # H disfluent
      datWithin_B <- datWithin_B %>% mutate(H_Disfluent = (H1+H4)/2)

  # L fluent
      datWithin_B <- datWithin_B %>% mutate(L_Fluent = (L2+L3)/2)
  # L Disfluent
      datWithin_B <- datWithin_B %>% mutate(L_Disfluent = (L1+L4)/2)


  # O fluent
      datWithin_B <- datWithin_B %>% mutate(O_Fluent = (O1+O4)/2)
  # O Disfluent
      datWithin_B <- datWithin_B %>% mutate(O_Disfluent = (O1+O4)/2)
      
      
#combbine datasets
      datWithin <- rbind(datWithin_A,datWithin_B)

### Now we have avarges for all F and D conditions for all participants
      
#reshape data 
datWithin_Plot <- datWithin %>% gather(GroupKey, Ratings,H_Fluent,H_Disfluent,L_Fluent,L_Disfluent,O_Fluent,O_Disfluent)
```

```{r}
########################################################################
      # Within groups t test (same people accross conditions)
######################################################################## 

t.test(datWithin %>% pull(H_Fluent),
            datWithin %>% pull(H_Disfluent), paired = TRUE)  %>% tidy()

t.test(datWithin %>% pull(L_Fluent),
            datWithin %>% pull(L_Disfluent), paired = TRUE) %>% tidy()

t.test(datWithin %>% pull(O_Fluent),
            datWithin %>% pull(O_Disfluent), paired = TRUE) %>% tidy()
```


 
    
```{r}
#descriptives
datWithin %>% summarise(H_F_mean = mean(H_Fluent), H_D_mean = mean(H_Disfluent), 
                        H_F_sd = sd(H_Fluent), H_D_sd = sd(H_Disfluent),
                                    
                        L_F_mean = mean(L_Fluent), L_D_mean = mean(L_Disfluent), 
                        L_F_sd = sd(L_Fluent), L_D_sd = sd(L_Disfluent),
                          
                        O_F_mean = mean(O_Fluent), O_D_mean = mean(O_Disfluent), 
                        O_F_sd = sd(O_Fluent), O_D_sd = sd(O_Disfluent))
```

                                                                      
```{r}

# effect size
cohensD(datWithin %>% pull(H_Fluent),
            datWithin %>% pull(H_Disfluent), method='paired')

cohensD(datWithin %>% pull(L_Fluent),
            datWithin %>% pull(L_Disfluent), method='paired')

cohensD(datWithin %>% pull(O_Fluent),
            datWithin %>% pull(O_Disfluent), method='paired')

```

                                       


























```{r}
########################################################################
      # MEDIATION ANALYSIS
########################################################################

#setting up data 

#predictor column
datWithin_Plot <- datWithin_Plot %>% mutate(Predictor = case_when(GroupKey == "H_Fluent" ~ "Fluent",
                                                                  GroupKey == "L_Fluent" ~ "Fluent",
                                                                  GroupKey == "O_Fluent" ~ "Fluent",
                                                                  GroupKey == "H_Disfluent" ~ "Disfluent",
                                                                  GroupKey == "L_Disfluent" ~ "Disfluent",
                                                                  GroupKey == "O_Disfluent" ~ "Disfluent",
                                                                  NULL)) 
                                                                 
#spread 
dat_Mediation <- datWithin_Plot %>% spread(GroupKey, Ratings) 
  
# columns for H L and O
dat_Mediation <- dat_Mediation %>% mutate(Hireability = coalesce(H_Disfluent,H_Fluent)) %>% 
                                    mutate(Likeability = coalesce(L_Disfluent,L_Fluent)) %>% 
                                    mutate(Opinion = coalesce(O_Disfluent,O_Fluent))

#remove unecassary columns
dat_Mediation <- dat_Mediation %>% select(-c(H_Disfluent,H_Fluent,L_Disfluent,L_Fluent,O_Disfluent,O_Fluent)) 
  
```

mediation tutorial:
https://www.youtube.com/watch?v=bvn1sqTb74s&ab_channel=StatisticsofDOOM


x / predictor = Predictor
m / mediator = opinion
y /  DV = hireability 




```{r}
####regression

#regression for IV on hireability ratings 
output <- lm(Hireability~Predictor, data = dat_Mediation) 

summary(output)
```



    
    
```{r}
#bmlm package mediation

#dummy code predictor with integers
BM <- dat_Mediation %>% mutate(Predictor=recode(Predictor,'Fluent'='1','Disfluent'='0'))

BM$Predictor = as.numeric(BM$Predictor)
```

```{r}
#turning response id into numeric
BM$ID <- as.numeric(factor(BM$ResponseId, 
                  levels=unique(BM$ResponseId)))
```

#mean centering not used in final anlaysis 
```{r}
#within person mean centering test 
Q <- isolate(BM,            #dataframe
                 by = "ID", #column of values that identifies individuals
                 value = c("Opinion", "Hireability"))
```
```{r}
#within person mean centering
B <- isolate(BM,            #dataframe
                 by = "ID", #column of values that identifies individuals
                 value = c("Predictor", "Opinion", "Hireability"))
```

```{r}
#checking data type is correct
str(B)
```



///////////////////////////////////////////////////////
HIREABILITY
///////////////////////////////////////////////////////

#this may take a few minutes to run 
```{r}
#HIREABILITY MEDIATION
fitZ <- mlm(d = Q, 
           id = "ID",
           x = "Predictor",
            m = "Opinion",
             y = "Hireability",
           iter = 2000,
           cores = 4)
```
```{r}
mlm_summary(fitZ)
```

```{r}
mlm_path_plot(fitZ, level = .95, text = T,
              xlab = "   AV Quality.  \n0 = Low\n1 = High",
              mlab = "Ease of\nOpinion\n.   Formation   ",
              ylab = "    Hireability   \nRatings", digits = 2)
```


subject-level estimates

https://mvuorre.github.io/bmlm/articles/bmlm-blch9/bmlm-blch9.html
"We can also visualize the between-subject heterogeneity in the indirect effect. This is one of the most interesting features of 1-1-1 mediation: Because every subject has their own slope for the a-path and b-path, they each have their own indirect effect as well. Here, the subjects are displayed in order of the size of their indirect effect, and the indirect effect in on the y-axis. We can easily see that although some participants show something similar to the average mediated effect (shown in red
), others show no mediated effect and others show a mediated effect several times larger than what we found for the prototypical person."

```{r}

mlm_pars_plot(fitZ, 
              type = "coef", 
              pars = c("u_me", "me"),
              level = .8)
```

///////////////////////////////////////////////////////
LIKEABILITY
///////////////////////////////////////////////////////

```{r}
#LIKEABILITY MEDIATION
fitL <- mlm(d = Q, 
           id = "ID",
           x = "Predictor",
            m = "Opinion",
             y = "Likeability",
           iter = 2000,
           cores = 4)
```
```{r}
mlm_summary(fitL)
```

```{r}
mlm_path_plot(fitL, level = .95, text = T,
              xlab = "   AV Quality.  \n0 = Low\n1 = High",
              mlab = "Ease of\nOpinion\n.   Formation   ",
              ylab = "    Likeability   \nRatings", digits = 2)
```

```{r}
#individual subjects level graph 
mlm_pars_plot(fitL, 
              type = "coef", 
              pars = c("u_me", "me"),
              level = .8)

```











```{r}
########################################################################
      # Graph preperation
########################################################################

#create groups for facet wrapping graph 

datWithin_Plot$Rating_Type <- as.factor(ifelse(datWithin_Plot$GroupKey == "H_Fluent", "Hireability", 
                                        ifelse(datWithin_Plot$GroupKey == "H_Disfluent", "Hireability", 
                                        ifelse(datWithin_Plot$GroupKey == "L_Fluent", "Likeability", 
                                        ifelse(datWithin_Plot$GroupKey == "L_Disfluent", "Likeability", 
                                        ifelse(datWithin_Plot$GroupKey == "O_Fluent", "Opinion Formation", 
                                        ifelse(datWithin_Plot$GroupKey == "O_Disfluent", "Opinion Formation", "NULL")))))))

  #turn group key into fluent or disfluent

datWithin_Plot$Video_Type <- as.factor(ifelse(datWithin_Plot$GroupKey == "H_Fluent", "Fluent",
                                      ifelse(datWithin_Plot$GroupKey == "H_Disfluent", "Disfluent",
                                      ifelse(datWithin_Plot$GroupKey == "L_Fluent", "Fluent",
                                      ifelse(datWithin_Plot$GroupKey == "L_Disfluent", "Disfluent",
                                      ifelse(datWithin_Plot$GroupKey == "O_Fluent", "Fluent",
                                      ifelse(datWithin_Plot$GroupKey == "O_Disfluent", "Disfluent", "NULL")))))))
                                            
```

```{r}
########################################################################
      # WITHIN GROUPS GRAPH 
########################################################################

#original figure
ggplot (datWithin_Plot, aes (
			 y = Ratings,
			x = GroupKey)) + 
	geom_violin () +
geom_boxplot ( width = 0.1 ) 

#seperated variation
ggplot (datWithin_Plot, aes (
	y = Ratings,
	x = Video_Type)) + 
	
  geom_violin () +
  geom_boxplot ( width = 0.1 ) +
  facet_wrap(~Rating_Type)

##### within groups graph #########################
  ggplot (datWithin_Plot, aes (
	  y = Ratings,
	  x = Video_Type,
	
	  fill = as.factor(Video_Type))) + 
	
    geom_violin () +
  
      geom_boxplot ( width = 0.1) +
 
   
  #geom_jitter(show.legend = F, width = 0.2, shape = 20) +
    
   geom_jitter(aes(), 
     position = position_jitter(width = .3), alpha = 0.4 , shape = 20
     )  +

    facet_wrap(~Rating_Type) +
    theme_classic() + 
    scale_fill_discrete(guide="none") +
  
    labs (x= "Condition")

############################################################
```                             
library(gghalves)
install.packages("ggdist")
```{r}
###### the above graphs dont look great, so lets change it.
#graph package

library(ggdist)
library(extrafont)
```

```{r}

 ggplot (datWithin_Plot, aes (
	  y = Ratings,
	  x = Video_Type,
	  fill = as.factor(Video_Type))) +

  #half violin + boxplot  
  ggdist::stat_halfeye(

      #custamise bandwidth option       adjust = .5, 
      width = .6, 
      .width = 0, 
      justification = -.3) + 
  
    geom_boxplot(
      width = .27, 
     outlier.shape = NA) +
  
  
  #jittor over boxplot 
  geom_point(
    size = 1,
    alpha = .3,
    position = position_jitter(
    seed = 1, width = .1)) + 

  #more graphs to the left by removing left space
  coord_cartesian(xlim = c(1.2, NA), clip = "off") +
  
  
  facet_wrap(~Rating_Type) +
  #theme_classic() +
  theme_test() +
  theme(text=element_text(family="Times New Roman")) + 
  scale_fill_discrete(guide="none") +
  
  labs (x= "AV Quality",
        y = "Ratings of Candidates")

  

  


```

    ## add justified jitter from the {gghalves} package
  gghalves::geom_half_point(
    ## draw jitter on the left
    side = "l", 
    ## control range of jitter
    range_scale = .4, 
    ## add some transparency
    alpha = .3
  ) +
  














////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
INDEPENDENT GROUPS ANALYSIS
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
////////////////////////////////////////////////////////////////////////////////////////////////////////////////////

```{r}
#### INDEPENDENT GROUPS T TEST


#hireability
t.test(datNum %>% filter(group == "A") %>% pull(H1),
                      datNum %>% filter(group == "B") %>% pull(H1)) %>% tidy()

cohensD(datNum %>% filter(group == "A") %>% pull(H1),
        datNum %>% filter(group == "B") %>% pull(H1), method='unequal')
  
#likeability
 t.test(datNum %>% filter(group == "A") %>% pull(L1),
                      datNum %>% filter(group == "B") %>% pull(L1)) %>% tidy()
 
 cohensD(datNum %>% filter(group == "A") %>% pull(L1),
        datNum %>% filter(group == "B") %>% pull(L1), method='unequal')
 
#opinion formation    
 t.test(datNum %>% filter(group == "A") %>% pull(O1),
                      datNum %>% filter(group == "B") %>% pull(O1)) %>% tidy()
 
 cohensD(datNum %>% filter(group == "A") %>% pull(O1),
        datNum %>% filter(group == "B") %>% pull(O1), method='unequal')
```

```{r}
wilcox.test(datNum %>% filter(group == "A") %>% pull(H1),
                      datNum %>% filter(group == "B") %>% pull(H1), paired = F)
```


```{r}
#### INDEPENDENT GROUPS PLOTS


### hireability graph 1
#FD
ggplot (datNum, aes ( group = group, 
			 y = H1,
			 x = group)) + 
	geom_violin () +
  geom_boxplot ( width = 0.1 ) 

#H Video 1 coloured graph version 
datNum <- datNum %>% mutate(H1_name = case_when(group == "A" ~ "Fluent", group == "B"  ~ "Disfluent"))

ggplot (datNum, aes ( group = H1_name, 
			 y = H1,
			 x = H1_name,
			 fill = H1_name)) + 
	geom_violin () +
    
  #geom_jitter(width = 0.15, shape = 20, alpha = 0.5) +
  
  geom_jitter(aes(), 
     position = position_jitter(width = .2), alpha = 0.2 #, shape = 20
     )  +
  
  geom_boxplot ( width = 0.1 ) +
  
  theme_classic() + 
  scale_fill_manual(values = c("#f7766d", "#03bfc4"))  + 
  scale_fill_discrete(guide="none") +
  
  labs (x= "Video 1", y = 'Ratings')
```

```{r}

ggplot (datNum, aes ( group = H1_name, 
			 y = H1,
			 x = H1_name,
			 fill = H1_name)) + 

    
    #half violin + boxplot  
  ggdist::stat_halfeye(

      #custamise bandwidth option       adjust = .5, 
      width = .6, 
      .width = 0, 
      justification = -.3) + 
  
    geom_boxplot(
      width = .15, 
     outlier.shape = NA) +
  
  
  #jittor over boxplot 
  geom_point(
    size = 1,
    alpha = .3,
    position = position_jitter(
    seed = 1, width = .1)) + 

  #more graphs to the left by removing left space
  coord_cartesian(xlim = c(1.2, NA), clip = "off") +

  theme_classic() + 
  theme(text=element_text(family="Times New Roman")) + 
  scale_fill_manual(values = c("#f7766d", "#03bfc4"))  + 
  scale_fill_discrete(guide="none") +
  
  labs (x= "AV Quality", y = 'Hireability Ratings')






```


